---
title: "Lithuania project"
author: "RF"
output: 
    html_document: default
---

```{r setup}

#remotes::install_github("sizespectrum/mizerExperimental")
library(mizerExperimental)
library(tidyverse)
library(plotly)
library(assertthat)
```

```{r tuneParams, eval = FALSE}

tuneParams(NS_params)


```
```{r multiResourceParams}
library(mizerMR)
library(tibble)
resource_params <- tribble(
    ~resource,  ~kappa, ~lambda, ~r_pp, ~w_min, ~w_max,
 "Resource 1",    1e11,    2.13,     4,    NA ,   0.01,
 "Resource 2",    1e11,    2.05,    10,   1e-4,     NA
)

paramsMR <- setMultipleResources(NS_params, resource_params)
```



# TODO list

Check that every plot is mizerMR compatible!

add legend select  and return data to all plots


# Some comments

getting error when using mizerMR::plotSpectra() without a params MR object (using NS_params in that case)
Error in mizer::animateSpectra(params, species = species, wlim = wlim,  : 
  unused arguments (background = background, highlight = highlight)
  
  fishing not in NS_params@linecolour, I thought it was for some reasons. upgradeParams doesn't fix the issue

## 1. Extract plot functions 

There are several plots included on tabs in the tuneParams gadget that are coded straight into the gadget rather than being stand-alone mizer plot functions. The code should be extracted to produce the following plot functions:

now `plotDataFrame` requires scales package. not sure if important or installed with base R

```{r plotDataFrame}

#' Make a plot from a data frame
#' 
#' This is used internally by most plotting functions.
#' 
#' @param frame A data frame with at least three variables.
#'   The first three variables are used, in that order, as:
#'   1. Variable to be plotted on x-axis
#'   2. Variable to be plotted on y-axis
#'   3. Grouping variable
#' @param params A MizerParams object, which is used for the line colours and
#'   line types.
#' @param style The style of the plot. Availalble options are "line' for geom_line
#' and "area" for geom_area. Default is "line".
#' @param legend_var The name of the variable that should be used in the legend
#'   and to determine the line style. If NULL then the grouping variable is
#'   used for this purpose.
#' @param legend_format If not supplied (default is NULL), the legend will use the 
#' linecolour and linetype slot to be displayed. If ones want to plot something undefined,
#' legend format needs to be supplied with anything (work in progress)
#' @param wrap_var Optional. The name of the variable that should be used for
#'  creating wrapped facets.
#' @param xlab Label for the x-axis
#' @param ylab Label for the y-axis
#' @param xtrans Transformation for the x-axis. Often "log10" may be useful
#'   instead of the default of "identity".
#' @param ytrans Transformation for the y-axis.
#' @param y_ticks The approximate number of ticks desired on the y axis
#' @param highlight Name or vector of names of the species to be highlighted.
#' @keywords internal
#' @export
plotDataFrame <- function(frame, params, style = "line", xlab = waiver(), 
                          ylab = waiver(), xtrans = "identity", ytrans = "identity", 
                          y_ticks = 6, highlight = NULL, legend_format = NULL,
                          legend_var = NULL, wrap_var = NULL, wrap_scale = NULL) {
  assert_that(is.data.frame(frame),
              is(params, "MizerParams"))
  if (ncol(frame) < 3) {
    stop("The data frame needs to have at least 3 variables.")
  }
  
  var_names <- names(frame)
  x_var <- var_names[[1]]
  y_var <- var_names[[2]]
  group_var <- var_names[[3]]
  if (is.null(legend_var)) {
    frame$Legend <- frame[[group_var]]
    legend_var <- "Legend"
  } else {
    if (!(legend_var %in% var_names)) {
      stop("The `legend_var` argument must be the name of a variable ",
           "in the data frame.")
    }
  }
  # Need to keep species in order for legend
  if(is.null(legend_format)) # if legend is defined in params object. Not automated but user dependent for now
  {
    legend_levels <- 
      intersect(names(params@linecolour), frame[[legend_var]])
    frame[[legend_var]] <- factor(frame[[legend_var]], levels = legend_levels)
    
    linecolour <- params@linecolour[legend_levels]
    linetype <- params@linetype[legend_levels]
    linesize <- rep_len(0.8, length(legend_levels))
    names(linesize) <- legend_levels
    linesize[highlight] <- 1.6 
  } else { # default value if legend is not defined in params object
    # TODO use legend_format as dataframe place holder to supply below values over default
    legend_levels <- unique(frame$Legend)
    frame[[legend_var]] <- factor(frame[[legend_var]], levels = legend_levels)
    colfunc <- colorRampPalette(c("#F8766D","#7CAE00","#00BFCFC4","#C77CFF")) # 4 base ggpplot colors
    linecolour <- colfunc(length(legend_levels))
    linetype <- rep_len("solid", length(legend_levels))
    names(linetype) <- legend_levels
    linesize <- rep_len(0.8, length(legend_levels))
    names(linesize) <- legend_levels
    linesize[highlight] <- 1.6 
  }
  
  xbreaks <- waiver()
  if (xtrans == "log10") xbreaks <- log_breaks()
  ybreaks <- waiver()
  if (ytrans == "log10") ybreaks <- log_breaks(n = y_ticks)
  
  # The reason why below `group = species` is included in `ggplot()`
  # rather than in `geom_line` is because that puts it first in the
  # plotly tooltips, due to a bug in plotly.
  p <- ggplot(frame, aes(group = .data[[group_var]])) +
    scale_y_continuous(trans = ytrans, breaks = ybreaks,
                       labels = prettyNum, name = ylab) +
    scale_x_continuous(trans = xtrans, name = xlab)
  
  switch (style,
          "line" = {p <- p + 
            geom_line(aes(x = .data[[x_var]], y = .data[[y_var]],
                          colour = .data[[legend_var]], 
                          linetype = .data[[legend_var]], 
                          size = .data[[legend_var]])) +
            scale_colour_manual(values = linecolour) +
            scale_linetype_manual(values = linetype) +
            scale_size_manual(values = linesize)
          },
          "area" = {p <- p + 
            geom_area(aes(x = .data[[x_var]], y = .data[[y_var]],
                          fill = .data[[legend_var]])) +
            scale_fill_manual(values = linecolour)
          },
          {"unknown style selected"}
  )
  
  if (!is.null(wrap_var)) {
    if (!(wrap_var %in% var_names)) {
      stop("The `wrap_var` argument must be the name of a variable ",
           "in the data frame.")
    }
    p <- p + facet_wrap(wrap_var, scales = wrap_scale)
  }
  p
}

```



plotMort() (plot on “Death” tab)
    
    
    
```{r death_tab}


# TODO
# tests

plotDeath <- function(object, species = NULL, proportion = TRUE, return_data = FALSE)
{
  if (is(object, "MizerSim")) {
    params <- object@params
    params <- setInitialValues(params, object)
  } else if (is(object, "MizerParams")) {
    params <- validParams(object)
  }
  
  SpIdx <- factor(params@species_params$species,
                  levels = params@species_params$species)
  
  if(is.null(species)) species <- SpIdx
  plot_dat <- NULL
  for(iSpecies in species)
  {
  fish_idx_full <- (params@w_full >= params@species_params[iSpecies, "w_min"]) &
    (params@w_full <= params@species_params[iSpecies, "w_inf"])
  fish_idx <- (params@w >= params@species_params[iSpecies, "w_min"]) &
    (params@w <= params@species_params[iSpecies, "w_inf"])
  pred_rate <- params@interaction[, iSpecies] *
    getPredRate(params)[, fish_idx_full]
  fishing <- getFMort(params)[iSpecies, fish_idx]
  total <- colSums(pred_rate) + params@mu_b[iSpecies, fish_idx] + fishing
  ylab <- "Death rate [1/year]"
  background <- params@mu_b[iSpecies, fish_idx]
  if (proportion) {
    pred_rate <- pred_rate / rep(total, each = dim(pred_rate)[[1]])
    background <- background / total
    fishing <- fishing / total
    ylab <- "Proportion of all death"
  }
  # Make data.frame for plot
  plot_dat <-
    rbind(plot_dat,
      data.frame(w = params@w[fish_idx],
                 value = background,
                 Cause = "Background",
                 Prey = SpIdx[which(iSpecies == SpIdx)]),
      data.frame(w = params@w[fish_idx],
                 value = fishing,
                 Cause = "Fishing",
                 Prey = SpIdx[which(iSpecies == SpIdx)]),
      data.frame(w = rep(params@w[fish_idx], each = dim(pred_rate)[[1]]),
                 value = c(pred_rate),
                 Cause = SpIdx,
                 Prey = SpIdx[which(iSpecies == SpIdx)])
    )
  }
  
  if (return_data) return(plot_dat) 
  
  plotDataFrame(plot_dat, params, style = "area", xtrans = "log10", wrap_var = "Prey",
                xlab = "Size [g]", ylab = ylab)
}

plotlyDeath <- function(object,
                        species = NULL,
                        proportion = TRUE,
                        ...) {
  argg <- c(as.list(environment()), list(...))
  ggplotly(do.call("plotDeath", argg),
           tooltip = c("value", "Cause", "w"))
}

#plotlyDeath(NS_params)

```
if this shows what killed you, why is there some background predation here ahah?   It's background mortality!! Maybe change the name? 

the plotly version creates a NA in the legend, don't know why


plotResourceMort() (upper plot on “Resource” tab. Needs panels for multiple resources.)

```{r resource_tab1}

plotResourcePred <- function(object, proportion = TRUE)
{
  if (is(object, "MizerSim")) {
    params <- object@params
    params <- setInitialValues(params, object)
  } else if (is(object, "MizerParams")) {
    params <- validParams(object)
  }
  SpIdx <- factor(params@species_params$species,
                  levels = params@species_params$species)
  
  #How many backgrounds are being used? Assuming using only mizerMR for now for additional backgrounds
  if(!is.null(params@other_params$other)) 
  {
    plot_dat <- NULL
    for(iRes in 1:dim(params@other_params$other$MR$resource_params)[1])
    {
      select <- (params@other_params$MR$capacity[iRes,] > 0)
      pred_rate <- params@other_params$MR$interaction[,iRes] *
        getPredRate(params)[, select]
      total <- colSums(pred_rate)
      
      ylab <- "Death rate [1/year]"
      if (proportion) {
        pred_rate <- pred_rate / rep(total, each = dim(pred_rate)[[1]])
        ylab = "Proportion of predation"
      }
      # Make data.frame for plot
      plot_dat <- rbind(plot_dat,
                        data.frame(
                          w = rep(params@w_full[select], each = dim(pred_rate)[[1]]),
                          value = c(pred_rate),
                          Predator = SpIdx,
                          Resource = params@other_params$other$MR$resource_params$resource[iRes]
                        ))
    }
    plotDataFrame(plot_dat, params, style = "area", xtrans = "log10",
                  xlab = "Resource size [g]", ylab = ylab, 
                  wrap_var = "Resource", wrap_scale = "free")
  } else {        
    select <- (params@cc_pp > 0)
    pred_rate <- params@species_params$interaction_resource *
      getPredRate(params)[, select]
    total <- colSums(pred_rate)
    ylab <- "Death rate [1/year]"
    if (proportion) {
      pred_rate <- pred_rate / rep(total, each = dim(pred_rate)[[1]])
      ylab = "Proportion of predation"
    }
    # Make data.frame for plot
    plot_dat <- data.frame(
      w = rep(params@w_full[select], each = dim(pred_rate)[[1]]),
      value = c(pred_rate),
      Predator = SpIdx
    )
    plotDataFrame(plot_dat, params, style = "area", xtrans = "log10",
                  xlab = "Resource size [g]", ylab = ylab)
  }
}

plotlyResourcePred <- function(object,
                        proportion = TRUE,
                        ...) {
  argg <- c(as.list(environment()), list(...))
  ggplotly(do.call("plotResourcePred", argg),
           tooltip = c("value", "Predator", "w"))
}


```
This calculate the potential predation on background since it uses the carrying capacity as value, is that alright?

plotResourceLevel() (lower plot on “Resource” tab. Will get one line for each resource.)

```{r resource_tab2}

plotResource <- function(object, return_data = FALSE)
{
  if (is(object, "MizerSim")) {
    params <- object@params
    params <- setInitialValues(params, object)
  } else if (is(object, "MizerParams")) {
    params <- validParams(object)
  }
  #How many backgrounds are being used? Assuming using only mizerMR for now for additional backgrounds
  if(!is.null(params@other_params$other)) 
  {
    plot_dat <- NULL
    for(iRes in 1:dim(params@other_params$other$MR$resource_params)[1])
    {
      select <- (params@other_params$MR$capacity[iRes,] > 0)
      plot_dat <- rbind(plot_dat,
                        data.frame(
                          w = params@w_full[select],
                          value = params@initial_n_other$MR[iRes,select] / params@other_params$MR$capacity[iRes,select],
                          Resource = params@other_params$other$MR$resource_params$resource[iRes])
      )
    }
  } else {
    select <- (params@cc_pp > 0)
    plot_dat <- data.frame(
      w = params@w_full[select],
      value = params@initial_n_pp[select] / params@cc_pp[select],
      Resource = "Resource" # 3rd var for plotDataFrame()
    )
  }
  
  if(return_data) return(plot_dat)
  
  plotDataFrame(plot_dat, params, xtrans = "log10",
                xlab = "Resource size [g]", ylab = "Proportion of carrying capacity")
}

```


plotEnergyBudget() (upper plot on “Rates” tab, but in the same style as `plotDiet()` or `plotMort()`.)

```{r rate_tab}

plotEnergyBudget <- function(object , species = NULL, logarithmic = TRUE, return_data = FALSE)
{
     if (is(object, "MizerSim")) {
        params <- object@params
        params <- setInitialValues(params, object)
    } else if (is(object, "MizerParams")) {
        params <- validParams(object)
    }
          SpIdx <- factor(params@species_params$species,
                          levels = params@species_params$species)
          
           if(is.null(species)) species <- SpIdx
  plot_dat <- NULL
  for(iSpecies in species)
  {
        max_w <- params@species_params[iSpecies, "w_inf"]
        if (logarithmic) {
            min_w <- params@species_params[iSpecies, "w_min"]
        } else {
            min_w = params@species_params[iSpecies, "w_mat"] / 10 # min(1, params@species_params[iSpecies, "w_min"])
        }
        sel <- params@w >= min_w & params@w <= max_w
        len <- sum(sel)
        growth <- getEGrowth(params)[iSpecies, sel]
        growth_and_repro <- getEReproAndGrowth(params)[iSpecies, sel]
        metab <- params@metab[iSpecies, sel]
        income <- growth_and_repro + metab
        repro <- growth_and_repro - growth
        
        plot_dat <- rbind(plot_dat,
                          data.frame(
            w = rep(params@w[sel], 4),
            value = c(growth, income, metab, repro),
            Type = c(rep("Growth", len),
                     rep("Income", len),
                     rep("Metabolic loss", len),
                     rep("Reproduction", len)),
            Species = SpIdx[which(iSpecies == SpIdx)])
                 )
  }
  
  if(logarithmic) xtrans = "log10" else xtrans = "identity"
  
 pl <- plotDataFrame(plot_dat, params, style = "area", xlab = "Size [g]",
                ylab = "Rate [g/year]", xtrans = xtrans, wrap_var = "Species",
                wrap_scale = "free",legend_format = TRUE)

 sizeVline <- data.frame(
                        w_mat = params@species_params[species, "w_mat"], 
                        w_inf = params@species_params[species, "w_inf"],
                        y_coord = plot_dat %>% group_by(Species) %>% summarise(Value = max(value)),
                        Type = NA) # geon_text wants a group var for some reasons
 colnames(sizeVline)[3:4] <- c("Species", "y_coord")

 pl <- pl +
   geom_vline(data  = sizeVline, aes(xintercept = w_mat, group = Species), linetype = "dotted") +
   geom_vline(data  =sizeVline, aes(xintercept = w_inf, group = Species), linetype = "dotted") +
   geom_text(data = sizeVline, aes(x = w_mat, y = y_coord * 0.2, label = "\nMaturity"), angle = 90) +
   geom_text(data = sizeVline, aes(x = w_inf, y = y_coord * 0.2, label = "\nMaximum"), angle = 90)

if(return_data) return(list(plot_dat,sizeVline)) else return(pl)
}

plotlyEnergyBudget <- function(object,
                               species = NULL, 
                               logarithmic = TRUE,
                        ...) {
  argg <- c(as.list(environment()), list(...))
  ggplotly(do.call("plotEnergyBudget", argg),
           tooltip = c("value", "Type", "w"))
}


```

Text starts to be cropped with > 10 species, scaling needed?


plotCatch() (lower plot on “Catch” tab)

```{r catch_tab}

plotYield2 <- function(object)
{
       if (is(object, "MizerSim")) {
        params <- object@params
        params <- setInitialValues(params, object)
    } else if (is(object, "MizerParams")) {
        params <- validParams(object)
    }
  
  no_sp <- length(params@species_params$species)
        observed <- params@species_params$yield_observed
        if (is.null(observed)) observed <- 0
        
        biomass <- sweep(params@initial_n, 2, params@w * params@dw, "*")
        yield_model <- rowSums(biomass * getFMort(params))
        
        # selector for foreground species
        foreground <- !is.na(params@A)
        foreground_indices <- (1:no_sp)[foreground]
        yield_model <- yield_model[foreground_indices]
        observed <- observed[foreground_indices]
        
        # Make sure species ordering is preserved in the plot
        species <- factor(params@species_params$species[foreground],
                          levels = params@species_params$species[foreground])
        
        df <- rbind(
            data.frame(Species = species,
                       Type = "Observed",
                       Yield = observed),
            data.frame(Species = species,
                       Type = "Model",
                       Yield = yield_model)
        )
        df <- df[df$Yield > 0, ]
        ggplot(df) +
            geom_col(aes(x = Species, y = Yield, fill = Type),
                     position = "dodge") +
            theme(text = element_text(size = 12)) +
            theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
            scale_y_continuous(name = "Yield [g/year]", trans = "log10",
                               breaks = log_breaks())
    }


plotObservedYield <- function(object, species = NULL, catch = NULL, catch_x = "Weight", return_data = FALSE)
{
  if (is(object, "MizerSim")) {
    params <- object@params
    params <- setInitialValues(params, object)
  } else if (is(object, "MizerParams")) {
    params <- validParams(object)
  }
  SpIdx <- factor(params@species_params$species,
                  levels = params@species_params$species)
  if(is.null(species)) species <- SpIdx
  
  species <- which(params@species_params$species == species)
  params <- set_species_param_default(params, "a", 0.006)
  params <- set_species_param_default(params, "b", 3)
  
  plot_dat <- NULL
  for(iSpecies in species)
  {
    a <- params@species_params[iSpecies, "a"]
    b <- params@species_params[iSpecies, "b"]
    
    # Check whether we have enough catch data for this species to plot it
    is_observed <- sum(catch$species == iSpecies) > 3
    
    # To choose the range of sizes over which to plot we look at the range
    # of sizes for which a non-zero catch was observed. If no catch was
    # observed for the species, we use the range from w_mat/100 to w_inf.
    if (is_observed) {
      if ("length" %in% names(catch)) {
        l_min = min(catch$length[catch$species == iSpecies])
        w_min = a * l_min ^ b
        l_max = max(catch$length[catch$species == iSpecies])
        w_max = a * l_max ^ b
      } else {
        w_min = min(catch$weight[catch$species == iSpecies])
        w_max = max(catch$weight[catch$species == iSpecies])
      }
      w_min_idx <- sum(params@w < w_min)
      w_max_idx <- sum(params@w <= w_max)
    } else {
      w_min_idx <- sum(params@w < (params@species_params$w_mat[iSpecies] / 100))
      w_max_idx <- sum(params@w <= params@species_params$w_inf[iSpecies])
    }
    w_sel <- seq(w_min_idx, w_max_idx, by = 1)
    w <- params@w[w_sel]
    l = (params@w[w_sel] / a) ^ (1 / b)
    
    catch_w <- getFMort(params)[iSpecies, w_sel] *
      params@initial_n[iSpecies, w_sel]
    # We just want the distribution, so we rescale the density so its area is 1
    if (sum(catch_w) > 0) catch_w <- catch_w / sum(catch_w * params@dw[w_sel])
    # The catch density in l gets an extra factor of dw/dl
    catch_l <- catch_w * b * w / l
    df <- data.frame(w, l, catch_w, catch_l, Type = "Model catch")
    
    # We also include the abundance density because that helps to understand
    # the catch density
    catch_w <- params@initial_n[iSpecies, w_sel]
    # We just want the distribution, so we rescale the density so its area is 1
    catch_w <- catch_w / sum(catch_w * params@dw[w_sel])
    # The catch density in l gets an extra factor of dw/dl
    catch_l <- catch_w * b * w / l
    abundance <- data.frame(w, l, catch_w, catch_l, Type = "Abundance")
    
    if (is_observed) {
      sel <- (catch$species == iSpecies)
      if ("length" %in% names(catch)) {
        l <- catch$length[sel]
        dl <- catch$dl[sel]
        catch_l <- catch$catch[sel]
        # normalise to a density in l
        catch_l <- catch_l / sum(catch_l * dl)
        # To get the density in w we need to divide by dw/dl
        w <- a * l ^ b
        catch_w <- catch_l / b * l / w
      } else {
        w <- catch$weight[sel]
        dw <- catch$dw[sel]
        catch_w <- catch$catch[sel]
        # normalise to a density in w
        catch_w <- catch_w / sum(catch_w * dw)
        # To get the density in l we need to divide by dl/dw
        l <- (w / a)^(1/b)
        catch_l <- catch_w * b / l * w
      }
      df <- rbind(df, data.frame(w, l, catch_w, catch_l,
                                 Type = "Observed catch"))
    }
    # From the abundance only keep values that are no larger than
    # the maximum of the other shown densities.
    if (catch_x == "Weight") {
      abundance <- subset(abundance, catch_w < max(df$catch_w))
    } else {
      abundance <- subset(abundance, catch_l < max(df$catch_l))
    }
    # Add the abundance to the data frame last so that it shows up
    # last also in legend
    df <- rbind(df, abundance)
    df$Species <- SpIdx[which(params@species_params$species[iSpecies] == SpIdx)]
    plot_dat <- rbind(plot_dat,df)
  }
  
  if (catch_x == "Weight") {
    
    pl <- plotDataFrame(plot_dat[,-c(2,4)], params, wrap_var = "Species", xtrans = "log10",
                        xlab = "Size [g]", ylab = "Normalised number density [1/g]",
                        wrap_scale = "free", legend_format = TRUE)
    
    sizeVline <- data.frame(
      w_mat = params@species_params[species, "w_mat"], 
      y_coord = plot_dat %>% group_by(Species) %>% summarise(Value = max(catch_w)),
      Type = NA) # geon_text wants a group var for some reasons
    colnames(sizeVline)[2:3] <- c("Species", "y_coord")
    
    pl <- pl +          
      geom_vline(data  = sizeVline, aes(xintercept = w_mat, group = Species), linetype = "dotted") +
      geom_text(data = sizeVline, aes(x = w_mat, y = y_coord * 0.9, label = "\nMaturity")) 
  } else {
    pl <- plotDataFrame(plot_dat[,-c(1,3)], params, wrap_var = "Species", xtrans = "log10",
                        xlab = "Size [cm]", ylab = "Normalised number density [1/cm]",
                        wrap_scale = "free", legend_format = TRUE)
    
    sizeVline <- data.frame(
      w_mat = (params@species_params[species, "w_mat"] /a) ^ (1 / b), 
      y_coord = plot_dat %>% group_by(Species) %>% summarise(Value = max(catch_l)),
      Type = NA) # geon_text wants a group var for some reasons
    colnames(sizeVline)[2:3] <- c("Species", "y_coord")
    
    pl <- pl +          
      geom_vline(data  = sizeVline, aes(xintercept = w_mat, group = Species), linetype = "dotted") +
      geom_text(data = sizeVline, aes(x = w_mat, y = y_coord * 0.9, label = "\nMaturity")) 
  }
  if(return_data) return(list(plot_dat,sizeVline)) else return(pl)
}


```



plotDiet() (panelled by species)


```{r plotDiet}

#' Get diet of predator at size, resolved by prey species
#'
#' Calculates the rate at which a predator of a particular species and size
#' consumes biomass of each prey species and resource.
#' The diet has units of grams/year.
#'
#' Returns the rates \eqn{D_{ij}(w)} at which a predator of species \eqn{i}
#' and size \eqn{w} consumes biomass from prey species \eqn{j}. This is
#' calculated from the predation kernel \eqn{\phi_i(w, w_p)},
#' the search volume \eqn{\gamma_i(w)}, the feeding level \eqn{f_i(w)}, the
#' species interaction matrix \eqn{\theta_{ij}} and the prey abundance density
#' \eqn{N_j(w_p)}:
#' \deqn{
#' D_{ij}(w, w_p) = (1-f_i(w)) \gamma_i(w) \theta_{ij}
#' \int N_j(w_p) \phi_i(w, w_p) w_p dw_p.
#' }
#' The prey index \eqn{j} runs over all species and the resources. It also runs
#' over any extra ecosystem components in your model for which you have
#' defined an encounter rate function. This encounter rate is multiplied by
#' \eqn{1-f_i(w)} to give the rate of consumption of biomass from these extra
#' components.
#'
#' This function performs the same integration as
#' [getEncounter()] but does not aggregate over prey species, and
#' multiplies by \eqn{1-f_i(w)} to get the consumed biomass rather than the
#' available biomass. Outside the range of sizes for a predator species the
#' returned rate is zero.
#'
#' @param params A \linkS4class{MizerParams} object
#' @param n A matrix of species abundances (species x size).
#' @param n_other A list of abundances for other dynamical components of the
#'   ecosystem
#' @param proportion If TRUE (default) the function returns the diet as a
#'   proportion of the total consumption rate. If FALSE it returns the
#'   consumption rate in grams per year.
#'
#' @return An array (predator species  x predator size x
#'   (prey species + resources) )
#' @export
#' @family summary functions
#' @concept summary_function
#' @seealso [plotDietMR()]
getDietMR <- function (params, n = initialN(params), n_pp = initial
                       n_other = initialNOther(params), proportion = TRUE)
{
    params <- validParams(params)
    species <- params@species_params$species
    no_sp <- length(species)
    no_w <- length(params@w)
    no_w_full <- length(params@w_full)
    no_other <- dim(n_other$MR)[1]
    other_names <- rownames(n_other$MR)

    assert_that(identical(dim(n), c(no_sp, no_w)), dim(n_other$MR)[2] == no_w_full)
    diet <- array(0, dim = c(no_sp, no_w, no_sp + no_other),
                  dimnames = list(predator = species, w = dimnames(params@initial_n)$w,
                                  prey = c(as.character(species), other_names)))
    idx_sp <- (no_w_full - no_w + 1):no_w_full

    if(!is.null(comment(params@pred_kernel))) {
        ae <- matrix(params@pred_kernel[, , idx_sp, drop = FALSE],
                     ncol = no_w) %*% t(sweep(n, 2, params@w * params@dw,
                                              "*"))
        diet[, , 1:no_sp] <- ae

        for(iRes in 1:no_other)
        {
            diet[, , no_sp + iRes] <- rowSums(sweep(params@pred_kernel, 3,
                                                    params@dw_full * params@w_full * n_other$MR[iRes,], "*"), dims = 2)
        }
    }
    else {
        prey <- matrix(0, nrow = no_sp + no_other, ncol = no_w_full)
        prey[1:no_sp, idx_sp] <- sweep(n, 2, params@w * params@dw, "*")
        prey[(no_sp + 1):(no_sp + no_other), ] <- sweep(n_other$MR,2,
                                                        params@w_full * params@dw_full, "*")
        ft <- array(rep(params@ft_pred_kernel_e, times = no_sp + no_other) *
                        rep(mvfft(t(prey)), each = no_sp), dim = c(no_sp, no_w_full, no_sp + no_other))
        ft <- matrix(aperm(ft, c(2, 1, 3)), nrow = no_w_full)
        ae <- array(Re(mvfft(ft, inverse = TRUE)/no_w_full),
                    dim = c(no_w_full, no_sp, no_sp + no_other))
        ae <- ae[idx_sp, , , drop = FALSE]
        ae <- aperm(ae, c(2, 1, 3))
        ae[ae < 1e-18] <- 0
        diet[, , 1:(no_sp + no_other)] <- ae
    }

    inter <- cbind(params@interaction,resource_interaction(params))
    diet[, , 1:(no_sp+no_other)] <- sweep(sweep(diet[, , 1:(no_sp+no_other), drop = FALSE],
                                                c(1, 3), inter, "*"), c(1, 2), params@search_vol, "*")

    f <- getFeedingLevel(object = params, n = n, n_other = n_other)
    fish_mask <- n > 0
    diet <- sweep(diet, c(1, 2), (1 - f) * fish_mask, "*")
    if (proportion) {
        total <- rowSums(diet, dims = 2)
        diet <- sweep(diet, c(1, 2), total, "/")
        diet[is.nan(diet)] <- 0
    }
    return(diet)
}


#' Plot diet, resolved by prey species, as function of predator at size.
#'
#' `r lifecycle::badge("experimental")`
#' Plots the proportions with which each prey species contributes to the total
#' biomass consumed by the specified predator species, as a function of the
#' predator's size. These proportions are obtained with `getDietMR()`.
#'
#' Prey species that contribute less than 1 permille to the diet are suppressed
#' in the plot.
#'
#' @inheritParams plotSpectra
#' @param species The name of the predator species for which to plot the diet.
#'
#' @return A ggplot2 object, unless `return_data = TRUE`, in which case a data
#'   frame with the three variables 'w', 'Proportion', 'Prey' is returned.
#' @export
#' @seealso [getDietMR()]
#' @family plotting functions

plotDietMR <- function (object, species = NULL, time_range, wlim = c(1, NA), return_data = FALSE)
{
    if (is(object, "MizerSim")) {
        if (missing(time_range)) time_range <- max(as.numeric(dimnames(object@n)$time))
        time_elements <- get_time_elements(object, time_range)
        n <- apply(object@n[time_elements, , , drop = FALSE], 2:3, mean)
        n_other <- list()
        n_other$MR <- apply(simplify2array(object@n_other[time_elements, ]), 1:2, mean)
        params <- object@params
        diet <- getDietMR(params, n = n, n_other = n_other)
    } else if (is(object, "MizerParams")) {
        params <- object
        diet <- getDietMR(params)
    } else {
        stop("The first argument must be either a MizerSim or a MizerParams object")
    }

    plot_dat <- melt(diet)
    plot_dat <- plot_dat[plot_dat$value > 0.001, ]
    colnames(plot_dat) <- c("Predator", "size", "Prey", "Proportion")
    plot_dat$Prey <- factor(plot_dat$Prey, levels = rev(unique(plot_dat$Prey)))

    if (is.null(species))
        p <- ggplot(plot_dat) + facet_wrap(. ~ Predator, scales = "free")
    else p <- ggplot(dplyr::filter(plot_dat, Predator == species))

    legend_levels <- intersect(names(params@linecolour), plot_dat$Prey)
    p <- p + geom_area(aes(x = size, y = Proportion, fill = Prey)) +
        scale_x_continuous(limits = wlim, name = "Size [g]", trans = "log10") +
        scale_fill_manual(values = params@linecolour[legend_levels]) +
        theme(legend.position = "right", legend.key = element_rect(fill = "black"),
              panel.background = element_blank(), panel.grid.minor = element_line(color = "gray"),
              strip.background = element_blank())

    if (return_data)
        return(plot_dat)
    else return(p)
}

```



All these plot functions should follow the conventions for layout and for list of arguments of similar existing mizer plot functions.
have panels for `plotMort()`, `plotEnergyBudget()`, `plotCatch()` and `plotDiet()`. 

extend `plotDataFrame()` to also be able to produce the kind of stacked plots needed for `plotDiet()`,  `plotMort()`, `plotEnergyBudget()` and then use it in those functions


```{r}



```







6 hours

## 2. Create resource controls
Extend `resourceControlUI()` to also create a drop-down menu with the resource names to allow the user to select which resource to control. Extend `resourceControl()` so that it can handle this selector.

4 hours

## 3. Plot yield vs F 
Improve `getYieldVsF()` so that it runs faster, see https://github.com/sizespectrum/mizerExperimental/issues/32. This includes a function `getMaxF()`.
Then make a new tab to show `plotYieldVsF()` with a control for the resolution of curve.
12 hours

##4. Generate code 
Write each function call that the `tuneParams()` gadget executes to either change the params object or to update a plot to a file, so that sourcing that file can reproduce the tuning of the params object and also produce all the plots the user looked at while using the app. See https://github.com/sizespectrum/mizerExperimental/issues/23



